Vagueness and imprecise imitation in signaling games

### 2016-02-17 paper/version_05/paper.tex
Added some references, including to paper in preparation.

It is intuitive to think that linguistic and conceptual categories are orderly in such a manner.
For example, if you consider two people, one with a height of 2m and another with a height of 2.2m, both `tall', it would be difficult to defend considering a person with a height of 2.1m `short'.
Another example is that of color categorization.
The World Color Survey project~\citep{WCS} collected color naming data for 110 unwritten languages of 45 language families.
For the great majority of these languages a pattern can be observed: basic color terms are by and large convex~\citep{Regier07,Jager2010}.
It is premature to argue that these observations can be extended to \emph{all} cases of categorization.
However, for the cases where it does apply, the result of \citet{JagerMetzger2011:Voronoi-Languag} is interesting because it demonstrates that signaling can impose this kind of orderly categories on a metric space without that being the ulterior purpose of it all.

>>>>

It is intuitive to think that linguistic and conceptual categories are orderly in such a manner.
For example, if you consider two people, one with a height of 2m and another with a height of 2.2m, both `tall', it would be difficult to defend considering a person with a height of 2.1m `short'.
Another example is that of color categorization.
The World Color Survey project~\citep{CookKay2005:The-World-Color,WCS} collected color naming data for 110 unwritten languages of 45 language families.
For the great majority of these languages a pattern can be observed: basic color terms are by and large convex~\citep{Regier07,Jager2010}.
It is premature to argue that these observations can be extended to \emph{all} cases of categorization.
However, for the cases where it does apply, the result of \citet{JagerMetzger2011:Voronoi-Languag} is interesting because it demonstrates that signaling can impose this kind of orderly categories on a metric space without that being the ulterior purpose of it all.%
\footnote{For the concrete case of color categorization, see also \citet{JagerRooijvan-Rooij2007:Language-Struct} and \citet{Correia2015}}
